An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-18 poly-embed-journal/poly-embed-journal.tex
Adding more detail to OP subsection, and touching up theorem 3 and 4

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 04 Mar 2021
	\begin{itemize}
		\item Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4
		\item Flesh out and expand on Ordered Partition Example
		\item add paragraph of discussion on the requirements of polyhedral losses
\end{itemize}}

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration implies\jessiet{is equivalent to?} \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.  
While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.  
		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$.  A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.  We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

\section{Embedding properties}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?  Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.  Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.  I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}

@@

\btw{JESSIE: This needs more narrative text.  I also don't know if this should go in the Appendix, given it doesn't really connect to the rest of the paper, though I think the point it makes (surrogates work for nearly any indirectly elicited property) is worth having in the body.}

@@

\begin{theorem}\label{thm:ie-iff-embeds-refinement}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.  Rinse and repeat for vertices of the expected loss on all possible (finite) supports.  As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?  Unclear on that gap.}
	\jessie{Cut everything but last paragraph}
	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
%	
%	Now let $\Gamma := \Gamma[L]$.
%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
%	
%	Now consider $\Y'\subset \Y$.
%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
%	
%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}

	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

\begin{theorem}\label{cor:ie-sufficient}
	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\bar \psi$ such that $(L, \bar \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
\end{theorem}
\begin{proof}
	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$. \jessie{Relies on results in the next section...}
	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
	(We know such a link exists by refinement.)
	Consider $\tilde \psi := \psi \circ \psi'$.

>>>>

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 04 Mar 2021
	\begin{itemize}
		\item Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4
		\item Flesh out and expand on Ordered Partition Example - DONE
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
\end{itemize}}

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{agarwal2015consistent}).
Given feature space $\X$, fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.  
While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent with respect to 0-1 loss.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  %\raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
  \jessiet{Proof intuition in comment}
%	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
%		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.  
%		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
%		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
%	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
%	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
%	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$.  A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
%	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
%	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
%	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
%	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
%	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
	%\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.  We then use these enumerated reports to define a finite property $\gamma$ such that $u_i \in \Gamma(p) \implies i \in \gamma(p)$, and take the discrete loss values equal to original loss values at the enumerated points.}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

\section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?  Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.  Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.  I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}

@@

\btw{JESSIE: This needs more narrative text.}

@@

\begin{theorem}\label{thm:ie-iff-embeds-refinement}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	\jessiet{17 Mar 21: REVISIT THIS... only one direction of the proof now.}
	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.  Rinse and repeat for vertices of the expected loss on all possible (finite) supports.  As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?  Unclear on that gap.}
	\jessie{Cut everything but last paragraph}
	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
%	
%	Now let $\Gamma := \Gamma[L]$.
%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
%	
%	Now consider $\Y'\subset \Y$.
%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
%	
%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}

	%\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi:\reals^d \to \R$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.

	\jessie{Added 18 Mar 21}
	This suffices to prove both directions of the equality since there is a subtle use of the statement ``$\gamma'_{r'} = \prop{L}_{\varphi(r')}$ follows as a corollary of Proposition~\ref{prop:embed-trim}, and each direction of the statement follows from a subset inclusion of one of these two level sets. 
%\jessie{added 17 Mar 21}
%	The ``only if'' direction follows from an implication of refinement, as $L$ embedding $\gamma'$ refining $\gamma \implies L$ indirectly elicits $\gamma$
%	Take embedding $\varphi$ and calibrated link\jessiet{Implicit forward ref to Theorem~\ref{thm:eps-thick-calibrated}} $\psi':\reals^d \to \R'$, and consider that $\prop{L}_u = \gamma'_{\psi'(u)} \subseteq \gamma_{\psi(u)}$, where $\psi$ is inherent in the definition of refinement.

\end{proof}

\begin{theorem}\label{thm:poly-ie-implies-consistent}
	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then for any loss $\ell'$ eliciting $\gamma'$, there exists a link $\hat \psi$ such that $(L, \hat \psi)$ is calibrated, and therefore consistent, with respect to $\ell'$.
\end{theorem}
\begin{proof}
	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a finite elicitable property $\gamma:\simplex \toto \R$ which refines $\gamma'$.
	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$ by Theorem~\ref{thm:eps-thick-calibrated}. \jessiet{Forward ref}
	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
	(We know such a link exists by refinement.)
	Consider $\hat \psi := \psi \circ \psi'$.
